---
title: "learning"
author: "ML"
format: html
---
## SETUP Chunk
```{r setup}
library(tidyverse)
library(here)
library(snakecase)
library(fs)
source(here("R/functions.R"))
```

##Importing new data
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

## Exercise: Reading other files

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, ,
    n_max = 100
  )
```
## Exercise: Reading other files, case 2

```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
  )
```
## Exercise: Limit rows

```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = "unique",
    n_max = 100
  )
```

## Exercise: Create function

```{r}
#' Add two number together
#'
#' @param One number
#' @param Another number here
#'
#' @returns returns the sum of two numbers
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

## Exercise: create functions, continued

```{r}
#' Read in one nurses stress data file
#'
#' @param file_path path to a data file
#'
#' @returns outputs table with max 100 columns

read <- function(file_path) {
  data <- file_path |>
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
}
```

## Exercise: final function

```{r}
#' Test function
#'
#' @param file_path
#' @param max_rows
#'
#' @returns your taxes, fiscal year 1987

read <- function(file_path, max_rows = 100) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = max_rows
    )
  return(data)
}

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

##Using map

```{r}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files

hr_data <- hr_files |>
  map(read) |>
  list_rbind(names_to = "file_path_id")

hr_data
```

## Exercise: Convert map to function and use on sleep.

```{r}
read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(read) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```

## Excercise 18.6, maxrow argument in read_all function

```{r}
read_all <- function(filename, max_rows = 100) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(\(file) read(file, max_rows = max_rows)) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz", max_rows = 10)
read_all("HR.csv.gz", max_rows = 1000)
```

## Excercise 18.7 Extra stuff

```{r}
.DATASET_DIR <- here::here("data-raw/nurses-stress/") # 1

# In the function body of `read_all()`.
read_all <- function(filename, max_rows = 100) {
  files <- .DATASET_DIR |> # 2
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(\(file) read(file, max_rows = max_rows)) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz", max_rows = 10)
read_all("HR.csv.gz", max_rows = 1000)
```

## Excercise 19.2 Survey data 

```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

#

survey_data
hr_data
```

##Extract ID from filepath

```{r}
hr_data |>
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) |>
      str_remove("/stress/") |>
      str_remove("/"),
    .before = file_path_id
  ) |>
  select(-file_path_id)
```


##Function for particpant ID

```{r}
get_participant_id <- function(data) {
  data_with_id <- data |>
    mutate(
      id = str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) |>
        str_remove("/stress/") |>
        str_remove("/"),
      .before = file_path_id
    ) |>
    select(-file_path_id)
  return(data_with_id)
}

# How it will be used.
get_participant_id(hr_data)
```

##Working with across

```{r}
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id()

hr_data
```

```{r}
hr_data |>
  summarise(across(where(is.numeric), list(
    mean = mean,
    median = median,
    sd = sd
  )))
```

## Working with dates

```{r}
hr_data |>
  mutate(datetime = round_date(collection_datetime,
    unit = "minute"
  ))
```

## Summarising by groups


```{r}
hr_data |>
  mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime)
  )
```

```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()
survey_data
```

```{r}
survey_tidy <- survey_data |>
  mutate(
    date = mdy(date),
    start_datetime = as_datetime(paste(date, start_time)),
    end_datetime = as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) |>
  select(-c(date, start_time, end_time, duration))
```

```{r}
survey_tidy |>
  select(id, datetime_id, start_datetime, end_datetime) |>
  pivot_longer(c(start_datetime, end_datetime), names_to = NULL, values_to = "collection_datetime") |>
  group_by(pick(-collection_datetime)) |>
  complete(collection_datetime = seq(min(collection_datetime),
    max(collection_datetime),
    by = 60
  )) |>
  ungroup()
```


## Convert into two new functions 

```{r}
#' Date cleaning function
#'
#' @param Cleans up dates
#'
#' @returns a data frame

tidy_survey_dates <- function(data) {
  tidied <- data |>
    dplyr::mutate(
      date = lubridate::mdy(date),
      start_datetime = lubridate::as_datetime(paste(date, start_time)),
      end_datetime = lubridate::as_datetime(paste(date, end_time)),
      datetime_id = start_datetime,
      .before = start_time
    ) |>
    dplyr::select(-c(date, start_time, end_time, duration))
  return(tidied)
}

survey_data |>
  tidy_survey_dates()

## Function #2: Survey to long function

#' Conversion to longer
#'
#' @param time
#'
#' @returns data frame
survey_to_long <- function(data) {
  longer <- data |>
    dplyr::select(id, datetime_id, start_datetime, end_datetime) |>
    tidyr::pivot_longer(
      c(start_datetime, end_datetime),
      names_to = NULL,
      values_to = "collection_datetime"
    ) |>
    dplyr::group_by(dplyr::pick(-collection_datetime)) |>
    tidyr::complete(
      collection_datetime = seq(
        min(collection_datetime),
        max(collection_datetime),
        by = 60
      )
    ) |>
    dplyr::ungroup()
  return(longer)
}
```

## Joining datasets

```{r}
survey_long |> 
  left_join(survey_tidy)
survey_data

survey_long |> 
  right_join(survey_tidy)

survey_long |> 
  full_join(survey_tidy)



```

##Full join data

```{r}
nurses_stress <- survey_long |>
  full_join(survey_tidy) |> 
  full_join(hr_data)

nurses_stress |> 
  arrange(id, collection_datetime) |> 
  View()
```

??full_join







